---
title: "FinalProject"
author: "Group 3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tigerstats)
library(readr)
```

## Section 1 - Loading the data and Exploring the data

We have selected Bike dataset to perform exploration of the data. We start by loading the data into the R Markdown file

```{r}
bike_data <- read_csv("Cleaned_bike_data.csv",show_col_types = FALSE)
```


```{r}
summary(bike_data)
```

We can see that there are different columns in the table which are Model_name, Model_year, Kms_driven, Owner, Location, Mileage, Power and Price.

To determine the different types of the datatypes, we can use the str command in R. This command tells us the different types of data which is present in the datasheet.
```{r}
str(bike_data)
```

The different types of datatypes which are present in the dataset are numeric and charachter.  

To determine the null values in the table, we can use the built in method in R. 

```{r}
null_values <- sum(is.na(bike_data)) 
null_values
```

With the above method, we can see that there are 0 missing/Null values in the dataset.

## Part 2 - Graphical Overview

You can also embed plots, for example:

```{r pressure, echo=FALSE}
```

## Part 3 - Hypothesis Testing

This section is for hypothesis testing

## Part 4 - Linear Regression

This section is for Linear Regression.
